---
title: "R you ready?"
author: "Matthias Bannert"
date: "4/2/2019"
output: ioslides_presentation
widescreen: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Before you start... 

**... check the stack:**

- R 3.3.1+
- R Studio 1.0+
- R packages: tidyverse, data.table, knitr
- git (optional)

## Guess what...

**... the following code does:**

```{r,echo=T}
a <- 1+1
b <- 2+2
d <- a + b
e <- c(1,2,4)
```

## You got this right, don't you?

```{r,echo=T,eval=F}
a <- 1+1
b <- 2+2
d <- a + b
e <- c(1,2,4)
```

```{r}
a
b
d
e
```

## Guess what...

**... the following code does:**

```{r,echo=T}
m <- matrix(1:12,4,3)
d <- data.frame(col1 = 1:8,
                col2 = letters[1:8])
l <- list()
l$element_a <- a
l$element_m <- m
l$element_d <- d
```

## You got this right, don't you?

```{r,echo=T,eval=F}
m <- matrix(1:12,4,3)
```

```{r}
m
```

## You got this right, don't you?

```{r,echo=T,eval=F}
d <- data.frame(col1 = 1:8,
                col2 = letters[1:8])
```

```{r}
d
```

## You got this right, don't you?

```{r,echo=T,eval=F}
l <- list()
l$element_a <- a
l$element_m <- m
l$element_d <- d
```

```{r}
l
```

## You know all of those, don't you?

```{r,eval=F,echo=T}
?sum()
ls()
c()
matrix()
data.frame()
list()
head()
tail()
str()
function()
lapply()
```

## Are you familiar with your R Studio IDE?

- R Studio is NOT R.
- script window
- console
- file browser
- R Studio IDE Cheat Sheets
- .Rproj
